Forecasting the 2024 Election: Trump Dominates the South, Harris Leads in the Midwest

### 2024-10-22 paper/paper.qmd
committing text changes

# Additional Data Details
It is important to note that several states remain uncolored (in gray), indicating missing or incomplete polling data for those states. These uncolored states reflect the absence of reliable or sufficient polling information required for an accurate prediction. This underscores the limitations of the data used in the model, where predictions are only made for states with adequate polling coverage. As a result, certain regions lack predictions, which could be addressed by including more comprehensive polling data in future analyses.

@@

```
\newpage

>>>>

# Additional Data Details
Placeholder

@@
